GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Add 4 charts

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
\textbf{Balance Sheet}, \textbf{Income Statement} and \textbf{Form 10-Q}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in millions of \$)}
    \label{fig:amount-of-gdpr-fines}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR article}
    \label{fig:violations-by-article}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{net-income}
    \caption{Net Income of Meta Platforms, Inc.(in billions of \$)}
    \label{fig:net-income}
\end{figure}

\subsection*{Legal expenses}

% Investigate the costs incurred by Meta Platforms in legal proceedings related
% to GDPR non-compliance. This includes expenses associated with hiring legal
% counsel, litigation, settlement agreements, and any ongoing legal obligations.
% Analyze the financial impact of these legal expenses on the company's
% profitability.
% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/

@@

% advertising data

@@

@@

\subsection*{Reputational Damage}

% Assess the financial impact of reputational damage resulting from GDPR
% non-compliance. Investigate whether negative media coverage, public backlash,
% or loss of user trust have affected Meta Platforms' brand value or customer
% perception. Analyze any associated costs, such as brand recovery campaigns or
% decreased user acquisition rates.

@@

>>>>

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\usepackage{cite}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
\textbf{Balance Sheets}, \textbf{Income Statements} and \textbf{Form 10-Q}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in
    millions of
    \$)\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:amount-of-gdpr-fines}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR
    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:violations-by-article}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{net-income}
    \caption{Net Income of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:net-income}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{revenue}
    \caption{Revenue of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:revenue}
\end{figure}

@@

% Average revenue per person Trends in Our Monetization by Facebook User
% Geography page 46 - advertising

@@

% Daily Active People Monthly Active People Daily Active Users (DAUs) facebook -
% per region Monthly Active Users (MAUs) facebook - per region

@@

\section{Discussion}

% % Investigate the costs incurred by Meta Platforms in legal proceedings
% related to GDPR non-compliance. This includes expenses associated with hiring
% legal counsel, litigation, settlement agreements, and any ongoing legal
% obligations. Analyze the financial impact of these legal expenses on the
% company's profitability. Reputational Damage Assess the financial impact of
% reputational damage resulting from GDPR non-compliance. Investigate whether
% negative media coverage, public backlash, or loss of user trust have affected
% Meta Platforms' brand value or customer perception. Analyze any associated
% costs, such as brand recovery campaigns or decreased user acquisition rates.

@@

% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/
